Formatting Instructions for ICLR 2020 \\ Conference Submissions

### 2019-09-10 reports/iclr/paper.tex
Add CNN and Attention equations

@@

@@

@@

A convolution layer is defined by the size of its kernel
The output of one layer of convolution for an input $\mX \in \R^{W\times H \times C}$ is
% \begin{align}
%   \mX'[r,c] &= 
% \end{align}

\subsection{Self Attention Layer}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{lccc}
    \toprule
    Model&relative&sinusoids&learned\\
    \midrule
    \cite{vaswani17attentionisallyouneed} & & \checkmark\\
    \cite{radford2018gpt2} & & & \checkmark\\
    \cite{devlin2018bert} & & & \checkmark\\
    \cite{dai2019transformerxl} & \checkmark & \checkmark \\
    \cite{yang2019xlnet}  & \checkmark & \checkmark \\
    \midrule
    \cite{belloAttentionAugmentedConvolutional2019} & \checkmark & & \checkmark \\
    \cite{ramachandran2019standaloneselfattention} & \checkmark & & \checkmark \\
    % Images
    \bottomrule
  \end{tabular}
  \caption{Type of position encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
  When multiple types have been tried by the authors, we report the one advised.}
  \label{tab:relwork_attention}
\end{table}

>>>>

\usepackage{todonotes}
\setlength{\marginparwidth}{3.4cm}

@@

Attention mechanism were introduced in Neural Machine Translation to better handle long range dependencies and align pairs of sentences \citep{Bahdanau2015attention}.

@@

We briefly recall the formulation of standard CNN layers and Self-Attention layers using unified notation.

@@

A convolution layer is defined by its kernel size $K$ (assuming square kernel for simplicity), the number of input channel $C_{in}$ and the number of output channel $C_{out}$. 
It is parametrized by a kernel tensor $\tW~\in~\R^{K\times K \times C_{out} \times C_{in}}$ and a bias vector $\vb~\in~\R^{C_{out}}$.
Given an input image $\tX~\in~\R^{W\times H \times C}$ of width $W$, height $H$ and $C$ channels, 
the output of the convolution layer is given by,
%
\begin{align}
  \tY_{i,j,:} = 
  \vb 
  +
  \sum_{(m, n) \in \{\lfloor (K-1) / 2 \rfloor, \dots, \lfloor K / 2 \rfloor\}^2}
  \mW_{m,n,:,:}
  \tX_{i+m, j+n, :}
\end{align}
%

\subsection{Self-Attention Layer}

A Self-Attention layer is defined by its hidden dimension $d_{h}$ and its number of heads $K$. \todo{JB: same as size of the CNN kernel, we point that they are related ($K^2$) but need clarify notation} %
It is parametrized by
$\tW^Q \in \R^{K \times d \times d_{h}}$ query layer, $\tW^V \in \R^{K \times d \times d_{h}}$ key layer, $\tW^V \in \R^{K \times d \times d_{h}}$ value layer, a projection layer $\tW^Q \in \R^{K \times d_{h} \times d}$ and output layer $\mW^O \in \R^{(Kd_{h})\times d}$. 
%
Applied to an input $\mX \in \R^{T\times d}$, the output of the Self-Attention layer is computed as,
%
\begin{align}
  \mA_k &= \operatorname{softmax}
  \left(
    (\mX \mW_k^K)(\mX \mW_k^Q)^\top
  \right)\,, \\
  %
  \mH_{t,:} &= 
  \sum_{k \in {1,\dots, K}} 
  \mA_k
  \mX
  \mW_k^P
  \,,\\
  %
  \mY_{t,:} &= \mH_{t,:} \mW^O + \mX_{t,:}\,,
\end{align}
where the $\operatorname{softmax}(\cdot)$ is taken over all the dimensions of the tensor but the first one. For simplicity, we exclude the batch normalization layers.%
\todo{JB: check dimensions and readability}%

@@

\begin{table}[h]
  \centering
  \begin{tabular}{lccc}
    \toprule
    Model&relative&sinusoids&learned\\
    \midrule
    \cite{vaswani17attentionisallyouneed} & & \checkmark\\
    \cite{radford2018gpt2} & & & \checkmark\\
    \cite{devlin2018bert} & & & \checkmark\\
    \cite{dai2019transformerxl} & \checkmark & \checkmark \\
    \cite{yang2019xlnet}  & \checkmark & \checkmark \\
    \midrule
    \cite{belloAttentionAugmentedConvolutional2019} & \checkmark & & \checkmark \\
    \cite{ramachandran2019standaloneselfattention} & \checkmark & & \checkmark \\
    % Images
    \bottomrule
  \end{tabular}
  \caption{Types of position encoding used by transformers models applied to text (\emph{top}) and images (\emph{bottom}). 
  When multiple encoding types have been tried, we report the one advised by the authors.}
  \label{tab:relwork_attention}
\end{table}
